Mapping Microblogging Posts to Encyclopedia Articles

### 2011-02-21 trunk/lids/twittersearchwrap/paper/paper.tex

@@

\begin{figure}[htb]
  \centering
  \includegraphics[width=.6\linewidth]{architecture}
  \caption{System architecture}
  \label{fig:arch}
\end{figure}

@@

\begin{table}[ht*]
\centering
\begin{tabular}{ l }
Search term                    \\
\hline
\#s21 \\
Karlsruhe\\
\end{tabular}
\caption{Search terms}\label{tbl:terms}
\end{table}

>>>>

Methods performed by the implemented system can be grouped into five sequential
steps. 
In a first step the wrapper fetches the atom feed generated by the
twitter search api\footnote{\url{http://dev.twitter.com/doc/get/search}} to a
search query. The generated feed contains information about the 100 most recent
twitter posts and their authors which match the search query.

@@

\begin{figure}[htb]
  \centering
  \includegraphics[width=.6\linewidth]{architecture}
  \caption{System Architecture}
  \label{fig:arch}
\end{figure}

@@

%\begin{table}[ht*]
%\centering
%\begin{tabular}{ 1 }
%Search term                    \\
%\hline
%\#s21 \\
%Karlsruhe\\
%\end{tabular}
%\caption{Search terms}\label{tbl:terms}
%\end{table}
